%% ------------------------------ Abstrglst ---------------------------------- %%
\glsenablehyper
\begin{abstract}
  Renewed interest in advanced nuclear power reactors such as the 
  \gls{vtr} at \gls{inl} has encouraged enhanced 
  modeling of fast nuclear power reactors. Since their inception in the early 
  days of nuclear engineering with reactors such as at the \gls{ebr-i}
  and Fermi 1, many new modeling techniques have been developed. This work 
  seeks to introduce modern methods and multiphysics simulation of fast 
  reactors.

  In this work, the multigroup neutron diffusion equation is solved via the
  \gls{fem}, allowing for the use of unstructured and general meshes. By using 
  an unstructured mesh, physical phenomena such as thermal expansion can be 
  modeled and used to distort the mesh. Additionally, the \gls{fem} will allow 
  for simplified spatial refinement by means of both mesh refinement and the use 
  of higher-order methods without regenerating the mesh. Unique to this thesis 
  is the use of pentahedral wedge elements in the \gls{fem} mesh for
  three-dimension simulations. Wedge elements are selected for their natural 
  description of hexagonal geometry common to fast reactors.  

  Thermal feedback effects within a fast reactors are also modeled in this work.
  A simplified thermal hydraulic model is used, modeling both axial heat 
  convection and radial heat conduction. Temperatures from this model are used 
  to calculate temperature dependent neutron cross-sections and
  simulate reactivity feedback effects. Additionally, a thermal expansion 
  model is used to simulate the thermal expansion of fuel and structural 
  components within the reactor. Thermal feedback effects significantly impact
  reactor behavior and contribute to the passive safety of fast reactor designs
  as demonstrated in the experiments performed at \gls{ebr-ii}
  \cite{ebriitests}.
  
  Using the multiphysics models developed in this work, a typical fast reactor 
  is simulated at operating conditions. The models as implemented demonstrate 
  expected reactor behavior for a fast reactor. For the simulated reactor, 
  reactivity feedback coefficients are calculated which would not be possible 
  without a coupled multiphysics model. These results can be used to demonstrate
  the passive safety features and feedback effects of such a nuclear reactor.

\end{abstract}
\glsresetall

%% ---------------------------- Copyright page ------------------------------ %%
\makecopyrightpage

%% -------------------------------- Title page ------------------------------ %%
\maketitlepage

%% -------------------------------- Dedication ------------------------------ %%
\begin{dedication}
  \centering To the future of clean electricity.
\end{dedication}

%% -------------------------------- Biography ------------------------------- %%
\begin{biography}
  William C. Dawn was born and raised in Stafford, Virginia. He attended public
  schools there for his primary education, participating in the Commonwealth
  Governor's School in High School. William earned a Bachelor's of Science 
  degree in Nuclear Engineering from North Carolina State University (NC State)
  in May 2017. After his Master's degree, William will remain at NC State to 
  pursue a Ph.D. degree in Nuclear Engineering. 

  William is a fellow of the \gls{iup} facilitated by \gls{doe-ne}. During his 
  undergraduate and graduate careers, he has had the opportunity to work with 
  \gls{geh} and \gls{ornl}. William has also made contributions to the
  \gls{casl}.
\end{biography}
\glsresetall

%% ----------------------------- Acknowledgements --------------------------- %%
\begin{acknowledgements}
  This work would not have been possible without the help of friends and family.
  I would like to thank my Mom and Dad, Suzanne and Bill Dawn, for their
  patience, their listening, and their advice. Their support has helped to make
  this work a reality.

  I would also like to thank my advisor, Dr. Scott Palmtag. We have both learned
  tremendously during this process. His consistency and desire to know more have
  kept me busy these last few months and I am grateful.
\end{acknowledgements}

%% -------------------------------- Disclaimer ------------------------------ %%
\clearpage
\vspace*{\fill}
\begin{center}
  \mbox{\parbox{5in}{
  This material is based upon work supported under an Integrated
  University Program Graduate Fellowship. Any opinions, findings, conclusions,
  or recommendations expressed in this publication are those of the author and
  do not necessarily reflect the views of the Department of Energy Office of
  Nuclear Energy.
  }}
\end{center}
\vspace*{\fill}
\clearpage

\thesistableofcontents

\thesislistoftables

\thesislistoffigures

\clearpage
\printglossary[type=\acronymtype,title={LIST OF ACRONYMS},nonumberlist]
\addcontentsline{toc}{chapter}{LIST OF ACRONYMS}
\glsresetall
