\chapter{Summary, Conclusions, and Recommendations}
\label{ch:conclusions}

\section{Summary of Simulation Results}

  The purpose of this thesis is to simulate a fast nuclear power reactor at 
  operating conditions with coupled multiphysics feedback. The method
  developed allows for solution to the multigroup neutron diffusion equation for
  general unstructured mesh and an arbitrary energy group structure. The coupled 
  multiphysics models allows for inherent modeling thermal feedback effects 
  instead of using extremely simplified models or calculations by hand. By 
  including all multiphysics models in a single simulation suite, a user can 
  easily observe the interaction of physical phenomena and feedback.

  In \chref{ch:neutronDiffusion}, a rigorous and general framework is developed
  for solving the multigroup neutron diffusion equation via the \gls{fem} for
  unstructured mesh. Insights are provided into the use of both
  two-dimension triangular elements and three-dimensional wedge (pentahedral)
  elements. Both of these geometries are natural choices for fast reactors which 
  typically employ hexagonal geometries. Using the methods developed,
  \chref{ch:diffusionResults} then demonstrates code verification and solution
  solution verification and for both analytic and reactor benchmark problems. 
  The multigroup neutron diffusion solver as implemented is shown to converge to 
  the correct $\keff$ value and flux distribution at the correct convergence 
  rate.

  \chref{ch:thermalHydraulics} presents the details of the thermal hydraulic
  models employed. These models include an axial convection model and a radial
  conduction model. Temperatures resulting from these thermal hydraulic models
  are used to interpolate cross-section tables and update coolant density to 
  generate temperature-dependent cross-sections. The formulae for the 
  interpolation of temperature-dependent cross-sections are also provided.

  In \chref{ch:thermalExpansion}, a simplified thermal expansion model is
  presented. The model expands materials linearly assuming materials thermally
  expand as either HT9 Stainless-Steel structural material or U10Zr fuel 
  material. The model requires an \textit{a priori} assumption of material 
  temperatures but results are not highly sensitive to these temperatures due 
  to the magnitudes of thermal expansion coefficients.

  The culmination of these multiphysics models is presented in a coupled
  simulation in \chref{ch:coupledResults}. A typical fast reactor, presented in 
  a benchmark problem, is simulated \cite{abr}. Using the models developed, 
  reactivity coefficients can be estimated for an operating reactor. These 
  coefficients provide insights into dynamic reactor behavior and agree with 
  expected values. These reactivity coefficients also describe the mechanisms 
  for inherent safety in a fast reactor.

\section{Conclusions}
  
  It has been demonstrated that the \gls{fem} can be used to efficiently 
  simulate the power distribution in a nuclear power reactor. Use of the
  \gls{fem} has allowed for the local simulation of multiphysics effects within 
  elements. The \gls{fem} framework allows for intuitive storage coupling of
  multiphysics effects because physics simulations can all share the same mesh.

  By simulating thermal hydraulic feedback and thermal expansion 
  effects, reactivity effects are estimated. Prior to this work, the 
  simulation of feedback effects required either manual iteration between 
  thermal hydraulic calculations and a neutron diffusion solver or the use of 
  simplified estimates of temperatures. This work has demonstrated a practical
  implementation of fast reactor multiphysics simulations by utilizing the
  \gls{fem} and a finite element framework.
  
\section{Recommendations for Future Research}

  In addition to general efficiency improvements (e.g. increased use of sparse
  matrices and vectorization) future work includes code enhancements, added 
  features, and simulation of new reactors. Ultimately, the goal is to develop a
  reactor simulation suite that can be used by industry professionals to perform 
  core design optimization calculations and analyze dynamic reactor behavior. 

  \subsection{Depletion Capabilities}
    To serve as a useful reactor simulator, this suite must be expanded to 
    include depletion capabilities. The code as presented in this work can be 
    used to design and optimize a clean (i.e. cycle-zero) fast reactor. However,
    any practical reactor design must be capable of extended and continuous 
    operation during an operating cycle. Depletion calculations inform the 
    reactor design by establishing the required excess reactivity at the 
    beginning of cycle.  Control strategies must then be designed to control 
    this excess reactivity. 

    Depletion calculations require solving the Bateman equations and the
    associated matrix exponential system of equations. Preliminary 
    investigations have been conducted for the
    implementation of the \gls{cram} as the depletion solver \cite{cram}. The 
    \gls{cram} will be implemented using the \gls{fem} mesh. A subsequent mesh 
    study will be required to determine if it is possible to use a coarse mesh 
    for depletion or if the fine mesh must also be used in iosotopic depletion 
    calculations.

  \subsection{Higher Order Finite Elements}
    Recall the \gls{fem} as presented in \chref{ch:neutronDiffusion} employs
    only linear triangular and linear wedge elements. However, the \gls{fem} as 
    derived can be implemented for polynomials of arbitrary order. Work by 
    Hosseini \cite{Hosseini2013} suggests that for finite element solutions to 
    the multigroup neutron diffusion equation, quadratic elements provide a 
    significant reduction of error without the need to reduce the mesh spacing. 
    With linear finite elements, the \gls{fem} is second-order spatially 
    convergent. Quadratic finite elements convey third-order spatial convergence 
    and cubic finite elements convey fourth-order spatial convergence. 
    Incorporating higher order finite elements will allow for simple solution 
    refinement without mesh regeneration.

  \subsection{\texorpdfstring{\glsentrylong{spn}}{Simplified PN} Solution}
    The \gls{spn} equations can provide considerable accuracy compared to the
    diffusion equation by incorporating angular dependence of flux rather than
    assuming isotropic scalar flux. The \gls{spn} equations reduce to a system
    of diffusion-like equations. Work by Ryu and Joo has demonstrated that the
    \gls{fem} can be used to solve the \gls{spn} equations in general geometry
    \cite{Ryu2013}.
    Implementation of the \gls{spn} equations would require the development of a
    new solver but much of the \gls{fem} framework can be reused. Implementation
    of the \gls{spn} method could provide enhanced accuracy for full-scale
    reactor problems.

  \subsection{Encouraging Code Usage}
    The simulation suite is designed to be used for practical fast nuclear power
    reactor simulations. An important step in this code becoming practical is 
    its adoption by users. Encouraging the usage of the simulation package will
    allow for user feedback. Additionally, users employing the code in a variety
    of simulations will encourage the development of future features that may be
    necessary for unique reactor designs. Future possible reactors to be 
    simulated include the SuperPhenix benchmark and simulation of the
    \gls{ebr-ii} inherent safety demonstrations \cite{ebriitests}.
    
    \renewcommand{\thefootnote}{\fnsymbol{footnote}}
    Currently, the code is maintained in a private Github repository so it may 
    easily be shared in the future. The author may be contacted\footnotemark 
    for access to the repository. 

    \footnotetext{William C. Dawn: 
      \texttt{\href{mailto:wcdawn@ncsu.edu}{wcdawn@ncsu.edu}}}


\glsresetall
